\section{Conclusion}
\label{ch:Conclusion}

% TODO:
% - Is it complete?
% - Could it be improved?
% - Limits of this paper
% - Needs to be applied to more existing approaches
% - Are there any areas lacking research?

% Hier sollte kurz die eigene Arbeit zusammengefasst werden (Ansatz, verwendete Methoden sowie Art der Evaluation und Ergebnisse). 
% In diesem Fall ist es 
% (i) die Entwicklung eines Ansatzes zur Klassifikation von OA für SAS nach 6 Dimensionen. 
% (ii) exemplarische classification von 3 OA Arbeiten mithilfe des entwickelten Klassifikationsansatzes;

% Formal sollten_
% - keine Referenzen auf Arbeiten darin genannt werden (falls notwendig, gehöret dass normalerweise in den Abschnitt 'Related work' oder 'Introduction)
% - keine Aufzählung enthalten sein

% TODO: Themeneinordnung

While there are different approaches to classify and reason about \acrshort{sas}, three of which were highlighted by this paper,
there is no classification for \acrshort{oa} for \acrshort{sas}.
Because of this it is hard to compare different \acrshort{oa} and identify areas which require further research.
To solve this problem this paper focused on proposing a classification for \acrshort{oa} for \acrshort{sas}.

\noindent To accomplish this, chapter \ref{ch:Foundations} started by explaining how \acrshort{sas} work with two short examples
and also showed some of their limitations.
This was followed by chapter \ref{ch:SASClassification} which explored three different approaches
for classifying and reasoning about \acrshort{sas}.
Chapter \ref{ch:Proposal} then derived and proposed a classification for \acrshort{oa} based on the principles shown in the previous chapter.
Lastly, chapter \ref{ch:Existing} compared a selection of existing \acrshort{oa} by using the proposed classification.
The comparison was then used to draw some initial conclusions about \acrshort{oa}.

\noindent The first conclusion was that most \acrshort{oa} only use the systems runtime to perform optimizations.
This has the advantage of not needing to simulate the system and its environment which can be complex.
But because most \acrshort{oa} use machine learning for their optimizations,
this can lead to unexpected or unwanted behavior at the beginning of the systems runtime.
This disadvantage is especially present in \acrshort{oa} that use machine learning approaches
like Q-learning which actively explores the problem space to find optimal solutions.

\noindent The second conclusion was that only a few \acrshort{oa} search for problems which require optimization in areas of a \acrshort{sas}
besides the Adaptation Control. The other two areas that can be optimized: the Level and the Technique still require
research into how effective their optimization can be.

\noindent The last conclusion was that most \acrshort{oa} use centralized approaches for performing optimizations.
Because of this the usage of decentralized approaches still requires further research.

\noindent Even though the proposed classification helps with comparing the existing \acrshort{oa},
it does not help with comparing their performance.
This is a problem not only for \acrshort{oa} but for \acrshort{sas} as well.
There is currently no scientific way of comparing the performance of \acrshort{sas}.
Because of this the effect of \acrshort{oa} on \acrshort{sas} can also not be quantified.

\noindent Another problem that \acrshort{sas} and their \acrshort{oa} have is that
most of them are highly domain specific and only try to solve a single domain problem.
This means that domain independent \acrshort{sas} and \acrshort{oa} for them still require research.




% FIXME: remove old after refactor
% This paper proposed a classification for \acrlong{oa}[es] for \acrlong{sas}[s].
% The classification was derived from the same principles as the taxonomy for \acrlong{sas}[s]
% by Krupitzer et al., 2015 \cite*{SurveyOnEngineeringApproaches}.
% The main principles that were used to derive the classification are:
% \begin{itemize}[nosep]
%     \item The 5W+1H questions by Salehie and Tahvildari, 2009 \cite*{LandscapeAndResearchChallenges}.
%     \item The MAPE-K feedback loop which was created by Kephart and Chess, 2003 \cite*{VisionOfAutonomicComputing}.
% \end{itemize}

% To classify \acrshort{oa} the proposed classification provides six dimensions:
% Location, Time, Purpose, Approach, Technique and Reflective Adaptation Control.


% \noindent The Location dimension asks on which level optimizations in a \acrlong{sas} might be necessary.
% Time distinguishes between \acrshort{oa} that are performed during the design time of the system,
% during the run time or online phase of the system or approaches that optimize systems during their offline phase.
% The dimension of Purpose provides a reason for Optimizations to be performed.
% Approach determines who is responsible for optimizations
% and Technique states which parts of a \acrshort{sas} can be optimized.
% Lastly, the Reflective Adaptation Control classifies how optimizations are performed.

% \noindent After proposing a classification, it was exemplarily applied to three existing \acrshort{oa}.
% This is a part where further research is required. 
% The classification has to be applied to further existing approaches to verify its validity and completeness.

% \noindent By applying the classification to more approaches, 
% one could also gain a structured overview over existing approaches.
% This can be used to identify approaches that have not been explored yet.